\documentclass[a4paper,10pt]{article}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{tabularx}
\geometry{margin=0.5in}
\usepackage{enumitem}
\pagestyle{empty}

\begin{document}

{\centering
  {\LARGE \textbf{Benjamin Kozel}} \\[4pt]
  \small Atlanta, Georgia \quad | \quad (252) 327-6521 \quad | \quad benjaminlkozel@gmail.com \\[2pt]
  \small github.com/Zidgel \quad | \quad linkedin.com/in/ben-kozel \par
}

\vspace{0.2in}

\textbf{Education}
\vspace{0.05in}
\hrule
\vspace{0.05in}

\begin{tabularx}{\textwidth}{X r}
\textbf{Georgia Institute of Technology} & August 2024 – Present \\
Master of Science in Computer Science – Specialization: Machine Learning & GPA: 4.00 \\
Atlanta, GA\\
\end{tabularx}

\begin{tabularx}{\textwidth}{X}
\textit{Relevant Coursework}: Machine Learning, Deep Learning, Reinforcement Learning, High-Performance Computing, GPU Software/Hardware
\end{tabularx}

\vspace{0.1in}

\begin{tabularx}{\textwidth}{X r}
\textbf{North Carolina State University} & August 2018 – May 2022 \\
Bachelor of Science in Computer Engineering, Electrical Engineering & GPA: 3.85 \\
Raleigh, NC\\
\end{tabularx}

\vspace{0.1in}
\textbf{Skills}
\vspace{0.05in}
\hrule
\vspace{0.05in}

\begin{tabularx}{\textwidth}{@{} l X @{}}
\textbf{Languages:} & Python, C, C++, Bash, TypeScript, JavaScript \\
\textbf{Frameworks \& Tools:} & PyTorch, Hugging Face, LlamaCPP, Svelte, FastAPI, FAISS, Redis, Docker, Git, CMake, Make \\
\textbf{ML Techniques:} & RAG, clustering, Transformers, actor-critic RL, anomaly detection \\
\textbf{Infra \& DevOps:} & Linux, CI/CD pipelines (Docker + systemd), SSH, YAML, Redis \\
\textbf{Embedded Systems:} & BIOS/UEFI, memory training, SPI, I2C/I3C, UART \\
\end{tabularx}

\vspace{0.1in}
\textbf{Experience}
\vspace{0.05in}
\hrule
\vspace{0.1in}

\noindent
\begin{minipage}[t]{0.99\textwidth}
  \begin{tabularx}{\textwidth}{@{} X r @{}}
  \textbf{Montage Technology, Inc.} & April 2023 -- Present \\
  Software Engineer II & Atlanta, GA \\
  \end{tabularx}
\end{minipage}


\vspace{4pt}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
  \item Designed and deployed a Retrieval-Augmented Generation (RAG) pipeline using a 3B LLaMA model with LlamaCPP and PyTorch, integrating FAISS and Redis to improve response latency by 40\% and enhance internal DRAM specification search tooling.
  \item Developed a clustering-based anomaly detection system for DDR memory training telemetry, enabling early signal error detection and reducing validation turnaround.
  \item Built and deployed a web-based visualization platform using Svelte and FastAPI to display DDR margining and anomaly clustering results; adopted company-wide for memory debug and training updates.
  \item Engineered on-premise AI infrastructure, including requisition and provisioning of GPU servers, CI/CD pipeline setup, and containerized model deployment for internal inference tools.
  \item Contributed to BIOS/UEFI firmware for Intel platforms, optimizing DDR memory training algorithms, supporting PCIe Link Margining tools and 2D signal eye diagram generation.
\end{itemize}

\vspace{0.1in}

\noindent
\begin{minipage}[t]{0.99\textwidth}
  \begin{tabularx}{\textwidth}{@{} X r @{}}
  \textbf{Micron Technology, Inc.} & June 2022 -- February 2023 \\
Semiconductor Product Engineer & Boise, ID \\
  \end{tabularx}
\end{minipage}
\vspace{4pt}
\begin{itemize}[leftmargin=*, itemsep=0pt, topsep=0pt, parsep=0pt, partopsep=0pt]
  \item Developed and executed validation routines for DRAM training, margining, and signal integrity on pre-silicon and post-silicon hardware.
  \item Built Python-based tools for automating test reports and analyzing memory interface data across multiple configurations.
  \item Collaborated with hardware and firmware teams to root-cause DDR training failures, supporting cross-functional debug cycles.
\end{itemize}

\vspace{0.1in}
\textbf{Certificates}
\vspace{0.05in}
\hrule
\vspace{0.15in}

\begin{tabularx}{\textwidth}{@{}X@{}}
\noindent\textbf{Certificates:} Hugging Face Transformers Course Certificate, AWS Certified Cloud Practitioner,\\ Edge Impulse Certified Edge AI Developer
\end{tabularx}

\vspace{0.1in}
\textbf{Projects}
\vspace{0.05in}
\hrule
\vspace{0.05in}

\begin{tabularx}{\textwidth}{@{} X r @{}}
\textbf{Kozami} & 2025 -- Present \\
\end{tabularx}
\vspace{-4pt}
\noindent\textbf{Tools:} AWS, Reinforcement Learning, RTOS, C/C++, Networking, TinyML, STM32, Raspberry Pi
\vspace{0.1in}
\begin{itemize}[leftmargin=*, nosep]
  \item Developed a home-deployable AI-enhanced media streaming service running on a Raspberry Pi 5 (8GB) connected to a local NAS.
  \item Designed and trained a custom reinforcement learning agent to generate dynamic “bumpers”—TV clips synchronized with a wide range of music genres.
  \item Deployed the application on AWS for external use by family and friends; observed consistent engagement across multiple households.
  \item Integrated STM32 microcontroller with TinyML-based voice control for hands-free operation, using custom command detection and local inference.
  \item Tuned RTOS-level optimizations and system-level scheduling to ensure smooth real-time playback and inference on constrained hardware.
\end{itemize}


\newpage

\vspace{-2pt}

% \textbf{Projects}
% \begin{itemize}[leftmargin=*]
%   \item \textbf{Project Name}: Short description.
% \end{itemize}

% \textbf{Skills}
% \begin{itemize}[leftmargin=*]
%   \item Languages: X, Y, Z
%   \item Tools: X, Y, Z
% \end{itemize}

\end{document}